Timeliness of security updates for Android and Chrome

### 2014-02-07 securityupdates.tex
Switch authors around after taking to Daniel Wagner
Change title and add hypothesis
Adjust preamble

\documentclass[conference,a4paper,twoside]{IEEEtran}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}
\author{Daniel Thomas}
\begin{document}
\title{Security of deployed Android devices}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Daniel Wagner,
Daniel R.\ Thomas,
Alastair R.\ Beresford,
Andrew Rice}
\IEEEauthorblockA{
Computer Laboratory\\
University of Cambridge\\
Cambridge, United Kingdom\\
Firstname.Lastname@cl.cam.ac.uk
}
}

@@

>>>>

\documentclass[conference,a4paper,twoside]{IEEEtran}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}
\author{Daniel R.\ Thomas, Daniel Wagner, Alastair R.\ Beresford and Andrew Rice}

\newcommand{\percArdMarketShare}{XX\%}
\newcommand{\percArdInsec}{XX\%}
\newcommand{\percCrmMarketShare}{XX\%}
\newcommand{\percCrmInsec}{X\%}
\newcommand{\daNumManufacturers}{XX}
\newcommand{\daNumNetworkOperators}{XXX}

\begin{document}
\title{Timeliness of security updates for Android and Chrome}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Daniel R.\ Thomas,
Daniel Wagner,
Alastair R.\ Beresford,
Andrew Rice}
\IEEEauthorblockA{
Computer Laboratory\\
University of Cambridge\\
Cambridge, United Kingdom\\
Firstname.Lastname@cl.cam.ac.uk
}
}

@@

% Hypothesis
% Attempts at fine grained restrictions on running arbitrary code are hampered by updates for security vulnerabilities not reaching uers in a timely fashion.
